---
title: "Health ABC Demo"
author: "Wassim Tarraf"
date: "11/3/2021"
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

# Upload packages
```{r setup, message=FALSE}
library(tidyverse)
library(haven)
library(dplyr)
library(tidyr)
library(labelled)
library(ggplot2)
library(magrittr)
library(naniar)
library(jstable)
library(summarytools)
library(tableone)
```


# Read and merge the data from wave 1
```{r, message=FALSE, warning=FALSE, results='hide'}
# Read the data
### Note: The following (lines 24-63) can be made more efficient by running through a loop
## list the names
## Change the path to correspond with local
# setwd("/Users/rrooks/Dropbox/MCCFAD Statistics Team work with R Rooks/Health ABC data 10.15.2021/")
###
base_path <- Sys.getenv("USERPROFILE")
data_path <- file.path(base_path, "/The University of Colorado Denver/Rooks, Ronica - Health ABC data 10.15.2021/")
setwd(data_path)
###
temp1 = list.files(path="Year 1",pattern="*.sas7bdat")
temp10 = list.files(path="Year 10",pattern="*.sas7bdat")
temp3 = list.files(path = "Year 3",pattern = "*.sas7bdat")
temp5 = list.files(path="Year 5",pattern="*.sas7bdat")
temp7 = list.files(path = "Year 7",pattern = "*.sas7bdat")
temp8 = list.files(path="Year 8",pattern="*.sas7bdat")
temp9 = list.files(path="Year 9",pattern="*.sas7bdat")
temp11 = list.files(path="Year 11",pattern="*.sas7bdat")
temp12 = list.files(path="Year 12",pattern="*.sas7bdat")
temp13 = list.files(path="Year 13",pattern="*.sas7bdat")
temp16 = list.files(path="Year 16",pattern="*.sas7bdat")
tempoutcm = list.files(path="Outcomes",pattern="*.sas7bdat")
tempsubstdy = list.files(path="Substudies",pattern="*.sas7bdat")
tempgenetics= list.files(path="Genetics",pattern="*.sas7bdat")
# tempinc = list.files(path="Health ABC SAS Incident Dementia code",pattern="*.sas7bdat")
tempinc = list.files("D:/Projects/Consulting Project 2022 - Demensia/Client Code", pattern = "*.sas7bdat")

 
# Read the data files from SAS into R
setwd("Year 1")
list2env(lapply(setNames(temp1[-which(temp1 == "one.sas7bdat")], make.names(gsub("*.sas7bdat$","", temp1[-which(temp1 == "one.sas7bdat")]))), read_sas), envir = .GlobalEnv)
setwd("../Year 10")
list2env(lapply(setNames(temp10, make.names(gsub("*.sas7bdat$","", temp10))), read_sas), envir = .GlobalEnv)
setwd("../Year 3")
list2env(lapply(setNames(temp3, make.names(gsub("*.sas7bdat$","", temp3))), read_sas), envir = .GlobalEnv)
setwd("../Year 5")
list2env(lapply(setNames(temp5, make.names(gsub("*.sas7bdat$","", temp5))), read_sas), envir = .GlobalEnv)
setwd("../Year 7")
list2env(lapply(setNames(temp7, make.names(gsub("*.sas7bdat$","", temp7))), read_sas), envir = .GlobalEnv)
setwd("../Year 8")
list2env(lapply(setNames(temp8, make.names(gsub("*.sas7bdat$","", temp8))), read_sas), envir = .GlobalEnv)
setwd("../Year 9")
list2env(lapply(setNames(temp9, make.names(gsub("*.sas7bdat$","", temp9))), read_sas), envir = .GlobalEnv)
setwd("../Year 11")
list2env(lapply(setNames(temp11, make.names(gsub("*.sas7bdat$","", temp11))), read_sas), envir = .GlobalEnv)
setwd("../Year 12")
list2env(lapply(setNames(temp12, make.names(gsub("*.sas7bdat$","", temp12))), read_sas), envir = .GlobalEnv)
setwd("../Year 13")
list2env(lapply(setNames(temp13, make.names(gsub("*.sas7bdat$","", temp13))), read_sas), envir = .GlobalEnv)
setwd("../Year 16")
list2env(lapply(setNames(temp16, make.names(gsub("*.sas7bdat$","", temp16))), read_sas), envir = .GlobalEnv)
setwd("../Outcomes")
list2env(lapply(setNames(tempoutcm, make.names(gsub("*.sas7bdat$","", tempoutcm))), read_sas), envir = .GlobalEnv)
setwd("../Substudies")
list2env(lapply(setNames(tempsubstdy, make.names(gsub("*.sas7bdat$","", tempsubstdy))), read_sas), envir = .GlobalEnv)
setwd("../Genetics")
list2env(lapply(setNames(tempgenetics, make.names(gsub("*.sas7bdat$","", tempgenetics))), read_sas), envir = .GlobalEnv)
# setwd("../Health ABC SAS Incident Dementia code")
setwd("D:/Projects/Consulting Project 2022 - Demensia/Client Code")
list2env(lapply(setNames(tempinc, make.names(gsub("*.sas7bdat$","", tempinc))), read_sas), envir = .GlobalEnv)



# Merge the data
## Merge the data for year 1
y1_ds <- left_join(ph, previncdz, by="HABCID") %>%
  left_join(., y1calc, by="HABCID") %>% 
  left_join(., y1clnvis, by="HABCID") %>%
  left_join(., y1mif, by="HABCID") %>%
  left_join(., y1mifcod, by="HABCID") %>%
  left_join(., y1rxcalc, by="HABCID") %>%
  left_join(., sixmovis, by="HABCID") %>%
  left_join(., y1read, by="HABCID") %>%
  left_join(., y1screen, by="HABCID") %>%
  left_join(., dna, by="HABCID") %>%
#below line includes DVs, IVs  
  select("HABCID", "MMMSCORE", "MMMFLAG", "DSS", "P4NC", "P4NI", "P4TST", "FPVWCURJ", "FPVWAHWR", "FPVWMOW", "FPVWCURV", "FPVWAHVW", 'FPVWMOV',
#below line includes CVs, APOEHAP for Apolipoprotein-e4 from Genetics folder and DNA sas file
  "RACE", "GENDER", "CV1AGE", "SITE", "HQSSOPIH", "EDUC", "FAMINC", "BMI", "MADATE", "Y1WTK",
  "BQDA12MO", "BQSCCGNO", "BQSCSNOW", "FPAC12MO", "FPHI12MO", "FPMI12MO",
  "HQSSRCLO", "HQSSFCLO", "APOEHAP")
#below line includes all variables to create count of chronic conditions
#  "Y1PCHD1", "Y1PCHD2", "Y1PCHD3", "Y1PCHF", "Y1PPAD", "Y1PDEPR1", "Y1PDIAB1", 
#  "Y1PGALLS", "Y1PHERNI", "Y1PGIBLD", "Y1PULCER", "Y1PHBP1", "Y1POAHIP", "Y1POAHND", "Y1POAKN",
#  "Y1POAOTH", "Y1POSTP1", "Y1PPROST", "Y1PPULCD")

# Combine with the dementia incidence data set using Health ABC data up to/incl year 11
y1plus <- left_join(y1_ds, habc_dementia, by="HABCID")

#this code from Wassim allows me to type variable names in lowercase
#bc R is case sensitive otherwise
names(y1plus) <- names(y1plus) %>% tolower

# Examine the generated data
head(y1plus)
table(y1plus$apoehap, y1plus$dementia) #produces a cross-tab bw apoehap(row) and dementia any time (column)
table(y1plus$faminc, exclude=NULL)
#1= less than 10K
#2=10K to 25K
#3=> 25K up to
#<50K
#4=≥ 50K
#5 - I want to recode the "no answer" to this category to prevent loss of 374 people in the sample
y1plus$faminc2 <- y1plus$faminc
y1plus$faminc2[is.na(y1plus$faminc2)] <- 5 # add level 5 to the factor for the NA-no answer
table(y1plus$faminc2, exclude=NULL)

table(y1plus$site, exclude=NULL)
```

# Variable management
```{r}
# Make changes to data set
# Recode the work and volunteer variables so that 7,8 are replaced with missing to focus on 0=No, 1=Yes

y1plus <- y1plus %>% mutate(r_fpvwcurj=fpvwcurj, r_fpvwcurv=fpvwcurv) %>% 
  replace_with_na(replace = list(r_fpvwcurj = c(7),
                             r_fpvwcurv = c(7, 8)))
  
  

# Variables of interest
vars <- c("dementia", "r_fpvwcurj","r_fpvwcurv", "race", "gender", "cv1age", "educ", "faminc2", "site", "apoehap")
covars <- c("r_fpvwcurj","r_fpvwcurv", "race", "gender", "cv1age", "educ", "faminc2", "site", "apoehap")
catvars <- c("r_fpvwcurj","r_fpvwcurv", "race", "gender", "educ", "faminc2", "site", "apoehap")
  
# Examine missing patterns
gg_miss_var(y1plus %>% select(vars)) + theme_bw() 
gg_miss_upset(y1plus %>% select(vars))

# Generate a descriptive Table
# Overall descriptives
print(dfSummary(y1plus %>% select(vars), plain.ascii = FALSE, style = "grid", 
                 graph.magnif = 0.6, valid.col = FALSE),  method = 'render')

# Descriptives by dementia status
CreateTableOne(vars = covars, strata = c("dementia"), data = y1plus,
                            factorVars = catvars)
```

# Split data by gender
```{r}
# Generate male and female 
y1plus_m <- y1plus %>% filter(gender==1)
y1plus_f <- y1plus %>% filter(gender==2)
```


# Modeling Total combined males and females
```{r}
# Fit a series of logistic regression models: Work

dem.m1.work <- glm(dementia ~ factor(r_fpvwcurj), data = y1plus, family = binomial)
dem.m2.work <- glm(dementia ~ factor(r_fpvwcurj) + factor(race) + factor(gender) + cv1age + factor(educ) + factor(site) + factor(faminc2), data = y1plus, family = binomial)
dem.m3.work <- glm(dementia ~ factor(r_fpvwcurj) + factor(race) + factor(gender) + cv1age + factor(educ) +  factor(site) + factor(faminc2) + factor(apoehap), data = y1plus, family = binomial)

# Examine Summaries of Models
summary(dem.m1.work)
summary(dem.m2.work)
summary(dem.m3.work)


# Combine the data frames to plot the ORs and CIs
rbind(m1.work, m2.work, m3.work) %>% filter(estimate=="factor(r_fpvwcurj)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.work", "m2.work", "m3.work"), labels=c("M1", "M2", "M3")))) +
  geo# You can add several post-hoc steps here (I only include the plots of estimates)

# Collect ORs, 95% CIs, and p-values in data frames
# Model 1
m1.work <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m1.work), confint(dem.m1.work))), digits=2),round(coef(summary(dem.m1.work))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m1.work") %>%  add_rownames(., var = "estimate")
# Model 2
m2.work <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m2.work), confint(dem.m2.work))), digits=2),round(coef(summary(dem.m2.work))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m2.work") %>%  add_rownames(., var = "estimate")
# Model 3
m3.work <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m3.work), confint(dem.m3.work))), digits=2),round(coef(summary(dem.m3.work))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m3.work") %>%  add_rownames(., var = "estimate")


# Combine the data frames to plot the ORs and CIs
rbind(m1.work, m2.work, m3.work) %>% filter(estimate=="factor(r_fpvwcurj)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.work", "m2.work", "m3.work"), labels=c("M1", "M2", "M3")))) +
  geom_point(aes(y=OR), shape=21, size=2) +
  geom_errorbar(aes(ymin=lci, ymax=uci), width=0.2) +
  geom_hline(yintercept=1, color="maroon", linetype = "dashed") +
  theme_bw() + 
  labs(x="Model", y="OR: Baseline Working") +
  ylim(0,2)


# Fit a series of logistic regression models: Volunteer
dem.m1.volun <- glm(dementia ~ factor(r_fpvwcurv) , data = y1plus, family = binomial)
dem.m2.volun <- glm(dementia ~ factor(r_fpvwcurv) + factor(race) + factor(gender) + cv1age + factor(educ) + factor(site) + factor(faminc2), data = y1plus, family = binomial)
dem.m3.volun <- glm(dementia ~ factor(r_fpvwcurv) + factor(race) + factor(gender) + cv1age + factor(educ) + factor(site) + factor(faminc2) + factor(apoehap), data = y1plus, family = binomial)

# Examine Summaries of Models
summary(dem.m1.volun)
summary(dem.m2.volun)
summary(dem.m3.volun)

# You can add several post-hoc steps here (I only include the plots of estimates)

# Collect ORs, 95% CIs, and p-values in data frames
# Model 1
m1.volun <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m1.volun), confint(dem.m1.volun))), digits=2),round(coef(summary(dem.m1.volun))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m1.volun") %>%  add_rownames(., var = "estimate")
# Model 2
m2.volun <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m2.volun), confint(dem.m2.volun))), digits=2),round(coef(summary(dem.m2.volun))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m2.volun") %>%  add_rownames(., var = "estimate")
# Model 3
m3.volun <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m3.volun), confint(dem.m3.volun))), digits=2),round(coef(summary(dem.m3.volun))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m3.volun") %>%  add_rownames(., var = "estimate")

# Combine the data frames to plot the ORs and CIs
rbind(m1.volun, m2.volun, m3.volun) %>% filter(estimate=="factor(r_fpvwcurv)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.volun", "m2.volun", "m3.volun"), labels=c("M1", "M2", "M3")))) +
  geom_point(aes(y=OR), shape=21, size=2) +
  geom_errorbar(aes(ymin=lci, ymax=uci), width=0.2) +
  geom_hline(yintercept=1, color="maroon", linetype = "dashed") +
  theme_bw() + 
  labs(x="Model", y="OR: Baseline Volunteering") +
  ylim(0,2)
```

# Male analyses for working and incident dementia (at anytime in the Health ABC data)
```{r}
# Fit a series of logistic regression models for men: Work

dem.m1.work.m <- glm(dementia ~ factor(r_fpvwcurj) , data = y1plus %>% filter(gender==1), family = binomial)
dem.m2.work.m <- glm(dementia ~ factor(r_fpvwcurj) + factor(race)  + cv1age + factor(educ) +  factor(site) + factor(faminc2), data = y1plus %>% filter(gender==1), family = binomial)
dem.m3.work.m <- glm(dementia ~ factor(r_fpvwcurj) + factor(race)  + cv1age + factor(educ) + factor(site) + factor(faminc2) + factor(apoehap), data = y1plus %>% filter(gender==1), family = binomial)

# Examine Summaries of Models
summary(dem.m1.work.m)
summary(dem.m2.work.m)
summary(dem.m3.work.m)

# You can add several post-hoc steps here (I only include the plots of estimates)

# Collect ORs, 95% CIs, and p-values in data frames
# Model 1
m1.work.m <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m1.work.m), confint(dem.m1.work.m))), digits=2),round(coef(summary(dem.m1.work.m))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m1.work.m") %>%  add_rownames(., var = "estimate")
# Model 2
m2.work.m <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m2.work.m), confint(dem.m2.work.m))), digits=2),round(coef(summary(dem.m2.work.m))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m2.work.m") %>%  add_rownames(., var = "estimate")
# Model 3
m3.work.m <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m3.work.m), confint(dem.m3.work.m))), digits=2),round(coef(summary(dem.m3.work.m))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m3.work.m") %>%  add_rownames(., var = "estimate")

# Combine the data frames to plot the ORs and CIs
g.work.m <- rbind(m1.work.m, m2.work.m, m3.work.m) %>% filter(estimate=="factor(r_fpvwcurj)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.work.m", "m2.work.m", "m3.work.m"), labels=c("M1", "M2", "M3")))) +
  geom_point(aes(y=OR), shape=21, size=2) +
  geom_errorbar(aes(ymin=lci, ymax=uci), width=0.2) +
  geom_hline(yintercept=1, color="maroon", linetype = "dashed") +
  theme_bw() + 
  labs(x="Model", y="OR: Baseline Working") +
  ylim(0,2) + ggtitle("Males")



# Female analyses for working and incident dementia (at anytime in the Health ABC data)
```{r}
# Fit a series of logistic regression models for women: Work

dem.m1.work.f <- glm(dementia ~ factor(r_fpvwcurj), data = y1plus_f, family = binomial)
dem.m2.work.f <- glm(dementia ~ factor(r_fpvwcurj) + factor(race) + cv1age + factor(educ) + factor(site) + factor(faminc2), data = y1plus_f, family = binomial)
dem.m3.work.f <- glm(dementia ~ factor(r_fpvwcurj) + factor(race) + cv1age + factor(educ) + factor(site) + factor(faminc2) + factor(apoehap), data = y1plus_f, family = binomial)

# Examine Summaries of Models
summary(dem.m1.work.f)
summary(dem.m2.work.f)
summary(dem.m3.work.f)

# You can add several post-hoc steps here (I only include the plots of estimates)

# Collect ORs, 95% CIs, and p-values in data frames
# Model 1
m1.work.f <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m1.work.f), confint(dem.m1.work.f))), digits=2),round(coef(summary(dem.m1.work.f))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m1.work.f") %>%  add_rownames(., var = "estimate")
# Model 2
m2.work.f <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m2.work.f), confint(dem.m2.work.f))), digits=2),round(coef(summary(dem.m2.work.f))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m2.work.f") %>%  add_rownames(., var = "estimate")
# Model 3
m3.work.f <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m3.work.f), confint(dem.m3.work.f))), digits=2),round(coef(summary(dem.m3.work.f))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m3.work.f") %>%  add_rownames(., var = "estimate")

# Combine the data frames to plot the ORs and CIs
g.work.f <- rbind(m1.work.f, m2.work.f, m3.work.f) %>% filter(estimate=="factor(r_fpvwcurj)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.work.f", "m2.work.f", "m3.work.f"), labels=c("M1", "M2", "M3")))) +
  geom_point(aes(y=OR), shape=21, size=2) +
  geom_errorbar(aes(ymin=lci, ymax=uci), width=0.2) +
  geom_hline(yintercept=1, color="maroon", linetype = "dashed") +
  theme_bw() + 
  labs(x="Model", y="OR: Baseline Working") +
  ylim(0,2) + ggtitle("Females")



# Fit a series of logistic regression models: Volunteer for men
dem.m1.volun.m <- glm(dementia ~ factor(r_fpvwcurv), data = y1plus %>% filter(gender==1), family = binomial)
dem.m2.volun.m <- glm(dementia ~ factor(r_fpvwcurv) + factor(race)  + cv1age + factor(educ) + factor(site) + factor(faminc2), data = y1plus %>% filter(gender==1), family = binomial)
dem.m3.volun.m <- glm(dementia ~ factor(r_fpvwcurv) + factor(race) + cv1age + factor(educ) + factor(site) + factor(faminc2) + factor(apoehap), data = y1plus %>% filter(gender==1), family = binomial)

# Examine Summaries of Models
summary(dem.m1.volun.m)
summary(dem.m2.volun.m)
summary(dem.m3.volun.m)

# You can add several post-hoc steps here (I only include the plots of estimates)

# Collect ORs, 95% CIs, and p-values in data frames
# Model 1
m1.volun.m <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m1.volun.m), confint(dem.m1.volun.m))), digits=2),round(coef(summary(dem.m1.volun.m))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m1.volun.m") %>%  add_rownames(., var = "estimate")
# Model 2
m2.volun.m <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m2.volun.m), confint(dem.m2.volun.m))), digits=2),round(coef(summary(dem.m2.volun.m))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m2.volun.m") %>%  add_rownames(., var = "estimate")
# Model 3
m3.volun.m <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m3.volun.m), confint(dem.m3.volun.m))), digits=2),round(coef(summary(dem.m3.volun.m))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m3.volun.m") %>%  add_rownames(., var = "estimate")

# Combine the data frames to plot the ORs and CIs
g.volun.m <- rbind(m1.volun.m, m2.volun.m, m3.volun.m) %>% filter(estimate=="factor(r_fpvwcurv)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.volun.m", "m2.volun.m", "m3.volun.m"), labels=c("M1", "M2", "M3")))) +
  geom_point(aes(y=OR), shape=21, size=2) +
  geom_errorbar(aes(ymin=lci, ymax=uci), width=0.2) +
  geom_hline(yintercept=1, color="maroon", linetype = "dashed") +
  theme_bw() + 
  labs(x="Model", y="OR: Baseline Volunteering") +
  ylim(0,2) + ggtitle("Males")
```
# Female analyses for volunteering
```{r}

# Fit a series of logistic regression models: Volunteering for women
dem.m1.volun.f <- glm(dementia ~ factor(r_fpvwcurv) , data = y1plus_f, family = binomial)
dem.m2.volun.f <- glm(dementia ~ factor(r_fpvwcurv) + factor(race) + cv1age + factor(educ) + factor(site) + factor(faminc2), data = y1plus_f, family = binomial)
dem.m3.volun.f <- glm(dementia ~ factor(r_fpvwcurv) + factor(race) + cv1age + factor(educ) + factor(site) + factor(faminc2) + factor(apoehap), data = y1plus_f, family = binomial)

# Examine Summaries of Models
summary(dem.m1.volun.f)
summary(dem.m2.volun.f)
summary(dem.m3.volun.f)

# You can add several post-hoc steps here (I only include the plots of estimates)

# Collect ORs, 95% CIs, and p-values in data frames
# Model 1
m1.volun.f <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m1.volun.f), confint(dem.m1.volun.f))), digits=2),round(coef(summary(dem.m1.volun.f))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m1.volun.f") %>%  add_rownames(., var = "estimate")
# Model 2
m2.volun.f <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m2.volun.f), confint(dem.m2.volun.f))), digits=2),round(coef(summary(dem.m2.volun.f))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m2.volun.f") %>%  add_rownames(., var = "estimate")
# Model 3
m3.volun.f <- as.data.frame(cbind(round(exp(cbind(OR = coef(dem.m3.volun.f), confint(dem.m3.volun.f))), digits=2),round(coef(summary(dem.m3.volun.f))[,4], digits=4))) %>% rename(lci="2.5 %", uci="97.5 %", pval="V4") %>% mutate(model="m3.volun.f") %>%  add_rownames(., var = "estimate")

# Combine the data frames to plot the ORs and CIs
g.volun.f <- rbind(m1.volun.f, m2.volun.f, m3.volun.f) %>% filter(estimate=="factor(r_fpvwcurv)1") %>% 
  ggplot(aes(x=factor(model, levels=c("m1.volun.f", "m2.volun.f", "m3.volun.f"), labels=c("M1", "M2", "M3")))) +
  geom_point(aes(y=OR), shape=21, size=2) +
  geom_errorbar(aes(ymin=lci, ymax=uci), width=0.2) +
  geom_hline(yintercept=1, color="maroon", linetype = "dashed") +
  theme_bw() + 
  labs(x="Model", y="OR: Baseline Volunteering") +
  ylim(0,2) + ggtitle("Females")


# Combining work estimates for males and females
ggpubr::ggarrange(g.work.m, g.work.f)

# Combining volunteering estimates for males and females
ggpubr::ggarrange(g.volun.m, g.volun.f)
```

